\documentclass[10pt,letterpaper,roman]{moderncv}
\usepackage[scale=0.8,margin=0.3in]{geometry}
\newgeometry{top=0.2in, right=0.4in, bottom=0.2in, left=0.4in}

\moderncvstyle{classic}
\moderncvcolor{blue}

\newcommand*{\mysection}[1]{%
  \vspace{2.5ex}% \@plus 1ex \@minus .2ex}%
  \phantomsection{}% reset the anchor for hyperrefs
  \addcontentsline{toc}{part}{#1}%
  % ... deleted
  \parbox[m]{\textwidth}{\sectionstyle{#1}}\\[1ex]}

\name{Elliot}{Wasem}
\title{Software Engineer}
\address{Nutley, NJ, USA}
\phone[mobile]{1-609-498-2128}
\email{elliotbielwasem@gmail.com}
\homepage{elliotwasem.xyz}
\social[linkedin]{elliot-wasem}
\social[github]{elliot-wasem}

\begin{document}

\makecvtitle 
\vspace{-0.4in}
\sethintscolumntowidth{\ }
\mysection{Education}
\textbf{Bachelors of Science, Computer Science}, Stevens Institute of Technology, \textit{Hoboken, NJ} \hfill 2017 -- 2020

\textit{\textbf{GPA} -- 3.49}

\begin{itemize}
  \item TA -- Algorithms, Concurrent Programming, Database Management Systems, Intro to Web Development
  \item Member of Upsilon Pi Epsilon: International Honor Society for the Computing and Information Disciplines
\end{itemize}

\mysection{Skills}
\textbf{Programming}:\space\space\space C, C++, Python, Erlang, Java, Rust, Bash, JavaScript\\
\textbf{Web \& Cloud}:\space\space\space HTML5, CSS, MySQL, Docker, GCloud\\
\textbf{Misc. Tech}:\space\space\space\space\space\space Git, Linux, Windows, Trello, Emacs, \LaTeX{}, VSCode


\mysection{Experience}
\textbf{Teaching Assistant, Stevens Institute of Technology} \textit{Hoboken, NJ} \hfill August 2018 -- Current
\begin{itemize}
\item Assistant for courses Algorithms, Concurrent Programming, Database Management Systems, Intro to Web Development
\item Created new assignments for students to nurture an understanding of the material
\item Assisted students gain an understanding for the topics taught in class
\item Graded students' understanding of the material on assignments and quizzes
\end{itemize}

\hfill

\textbf{Software Engineer, \href{https://dexteritydb.com}{DexterityDB}}, \textit{Hoboken, NJ} \hfill April 2018 -- Current
\begin{itemize}
\item Developed various parts of database storage engine, with most work done on a virtual filesystem.
\item Designed and built continuous integration tools such as automated build servers, benchmark servers, and various automation scripts to streamline daily workflow.
\item Implemented testing scripts to speed up the generation of data as the product was further developed.
\item Served as the company's Linux expert and server administrator.
\end{itemize}\space

\hfill

\textbf{Undergraduate Research Assistant, Stevens Institute of Technology}, Hoboken, NJ \hfill September 2018 -- December 2018
\begin{itemize}
\item Explored the possibility of extending eBPF from the network interfaces down to storage mediums.
\item Setup and maintained Ubuntu servers both for the head professor and for other researchers.
\end{itemize}

\hfill

\textbf{Wireless Team Lead, \href{https://www.marketsource.com/}{MarketSource, Target Mobile}} \textit{Princeton, NJ} \hfill September 2015 -- November 2016
\begin{itemize}
\item Managed new and existing accounts for Verizon Wireless, AT\&T, Sprint, and Comcast XFinity.
\item Maintained relations with Target management to ensure effective sales flow, fraud prevention, and organization.
\item Organized and maintained Target Mobile's inventory and assets.
\end{itemize}

\mysection{Projects}
\textbf{Personal Website} \textit{Hoboken, NJ} (HTML, CSS, JavaScript) \hfill June 2019 -- Current
\begin{itemize}
  %        \item My personal website tries to let the user experience the computer the way I do on a daily basis: through the commandline.
\item Implemented in ``vanilla'' JavaScript, it provides a handful of custom-implemented commands to let the user browse my credentials in a terminal fashion.
\item Designed to be a unique experience that speaks to my strengths using computers
\end{itemize}

\hfill

\textbf{TinyChat, Concurrent Programming, Stevens Institute of Tech}, \textit{Hoboken, NJ} (Erlang) \hfill June 2019 -- September 2019
\begin{itemize}
\item Designed and setup groundwork for assignment for students in the Fall 2019 semester.
\item Assignment is to create an IRC chat application, implemented completely in Erlang.
\item Purpose of assignment is to give students a full understanding of message passing.
  %        \item The project is designed such that it would only take a few lines more of code to turn this into a fully distributed, centralized messaging application. However for the purpose of this assignment, it was designed so that processes were all locally running on a single computer.
\end{itemize}

\hfill

\textbf{Personal Password Manager} \textit{Hoboken, NJ} (Rust) \hfill March 2019 -- July 2019
\begin{itemize}
\item Password manager implemented in Rust.
\item Uses \href{https://github.com/davatorium/rofi}{Rofi} as a graphical user interface.
\item Stored passwords locally in a secure manner, all locked behind a master password.
\end{itemize}

\hfill

\textbf{Virtual Filesystem}, DexterityDB \textit{Hoboken, NJ} (Rust) \hfill May 2018 -- August 2018
\begin{itemize}
\item Designed and implemented a virtual filesystem implemented in Rust.
\item Ensured that it was the minimum needed to work with the database software so as to run lean and efficiently.
\item Reduced the file descriptors needed open from upwards of a million down to just a small handful.
\end{itemize}

\end{document}
