\documentclass[12pt,letterpaper,roman]{moderncv}
\usepackage[scale=0.8,margin=1.5in]{geometry}
\newgeometry{top=1.0in, right=1.0in, bottom=1.0in, left=1.0in}

\moderncvstyle{classic}
\moderncvcolor{blue}

\newcommand*{\mysection}[1]{%
  \vspace{2.5ex}
  \phantomsection{}
  \addcontentsline{toc}{part}{#1}%
  \parbox[m]{\textwidth}{\sectionstyle{#1}}\\[1ex]}

\name{Elliot}{Wasem}
\title{Software Engineer}
\address{Lyndhurst, NJ, USA}
\phone[mobile]{1-609-498-2128}
\email{elliotbielwasem@gmail.com}
\homepage{elliotwasem.xyz}
\social[linkedin]{elliot-wasem}
\social[github]{elliot-wasem}

\begin{document}

\maketitle{}

\sethintscolumntowidth{\ }
Hello,\bigskip

I am a computer science major earning my Bachelor's of Science from Stevens
Institute of Technology late May of this year, and am seeking employment
beginning in mid to late August.\bigskip

As a software developer, I take a strong stance in favor of stability,
scalability, and efficiency over quick implementation, and it shows in my
code. I am very strong in low-level development, and my in-depth knowledge
of UNIX and UNIX-like (BSD, Linux, Solaris, etc.) systems and how their kernels
work allows me to take advantage of stability and performance optimizations that
otherwise may be overlooked. I have experience writing enterprise-level
software, and feel comfortable with creating scalable solutions that is just as
efficient running in a single node as communicating across distributed
systems.\bigskip

I have taken a course in systems administration which has allowed me to learn
enormous amounts about AWS, and has exposed me to many of the issues and
decisions surrounding managing servers, users, and software, as well as many of
the best practices therein.\bigskip

That is not to say that I am naive enough to think I know everything. I
regularly come across new topics for which I have no prior expertise off which
to work. This means that I am constantly learning and growing, and feel very
comfortable learning on the job, and considering many different plans of attack
before moving forward with a solution.\bigskip

I look forward to hearing more from you, and answering any further questions you
may have.\bigskip

Regards,

Elliot Wasem
\end{document}
