\documentclass[10pt,letterpaper,roman]{moderncv}
\usepackage[scale=0.8,margin=0.3in]{geometry}
\newgeometry{top=0.1in, right=0.4in, bottom=0.2in, left=0.4in}

\moderncvstyle{classic}
\moderncvcolor{blue}

\newcommand*{\mysection}[1]{
  \vspace{2.5ex}
  \phantomsection{}
  \addcontentsline{toc}{part}{#1}
  \parbox[m]{\textwidth}{\sectionstyle{#1}}\\[1ex]}

\name{Elliot}{Wasem}
\title{Software Engineer}
\address{Lyndhurst, NJ, USA}
\phone[mobile]{1-609-498-2128}
\email{elliotbielwasem@gmail.com}
\homepage{elliotwasem.xyz}
\social[linkedin]{elliot-wasem}
\social[github]{elliot-wasem}

\begin{document}

\makecvtitle 
\vspace{-0.6in}
\sethintscolumntowidth{\ }

\mysection{Education}
\textbf{Bachelors of Science, Computer Science}, Stevens Institute of
Technology, \textit{Hoboken, NJ} \hfill May, 2020\\
Castle Point Terrace, Hoboken, NJ 07030\\

\textit{\textbf{GPA} --- 3.6}

\begin{itemize}
  \item \textbf{Relevant courses}: Algorithms, Data Structures, Database
    Management Systems, Agile Methods, Concurrent Programming, Operating
    Systems, Web Programming, Advanced Programming in UNIX, Compiler Design,
    Systems Administration 
  \item \textbf{Senior Design, Computer Science}, \textit{first place}: Along
    with my team, created machine learning computer vision model for a shipping
    solution by Zebra Technologies. 
  \item \textbf{Upsilon Pi Epsilon}, member: International Honor Society for the
    Computing and Information Disciplines 
\end{itemize} \bigskip
\textbf{Transfer Credit}, Mercer County Community College, \textit{West Windsor,
  NJ} \hfill Jan 2015 --- Dec 2016\\
1200 Old Trenton Rd, West Windsor Township, NJ 08550\\
\textit{\textbf{GPA} --- 3.7}

\mysection{Skills}
\textbf{Programming}:\space\space\space C, C++, C\#, .NET, Python, Erlang, Java, Rust,
Bash, JavaScript, Ocaml\\
\textbf{Web \& Cloud}:\space\space\space AWS, GCloud, MySQL, Docker, HTML5,
CSS\\
\textbf{Misc. Tech}:\space\space\space\space\space\space UNIX, Git, Linux,
Windows, Trello, Emacs, \LaTeX{}, VSCode

\mysection{Experience}
\textbf{Software Engineer, DexGroup, LLC}, \textit{Remote} \hfill June 2020 --- Current\\
81 Arden Blvd, West Hempstead, NY 11552
\begin{itemize}
\item Designed and implemented human-computer interfaces for Amazon warehouses
  and facilities.
\item Worked with Ignition software to create visual elements and connect them
  to systems for the purpose of monitoring status and operation of various
  machines and devices.
\end{itemize}\space

\hfill

\textbf{Software Engineer, \href{https://dexteritydb.com}{DexterityDB}},
\textit{Hoboken, NJ} \hfill Apr 2018 --- May 2020\\
81 Arden Blvd, West Hempstead, NY 11552
\begin{itemize}
\item Used Rust programming language to develop database storage engine, with
  most work done on a virtual filesystem.
\item Reduced memory footprint of program by eliminating unnecessary memory
  allocation and usage.
\item Designed and created Linux server systems to run custom continuous
  integration tools written in Bash, Python, and R to provide on-demand binaries
  and running statistics as development progressed.
\item Implemented testing scripts to accelerate generation of data as the
  product was developed, cutting need for manual generation.
\item Handled DevOps tasks relating to our server system, providing expertise
  where others lacked in-depth understanding.
\end{itemize}\space

\hfill

\textbf{Teaching Assistant, Stevens Institute of Technology} \textit{Hoboken,
  NJ} \hfill Aug 2018 --- May 2020\\
Castle Point Terrace, Hoboken, NJ 07030
\begin{itemize}
\item Assistant for courses Algorithms, Concurrent Programming, Database
  Management Systems, Intro to Web Development.
\item Created new assignments for students to nurture an understanding of the
  material.
\item Assisted students in gaining an understanding for the topics taught in
  class.
\end{itemize}

\hfill

\textbf{Undergraduate Research Assistant, Stevens Institute of Technology},
\textit{Hoboken, NJ} \hfill Sep 2018 --- Dec 2018\\
Castle Point Terrace, Hoboken, NJ 07030
\begin{itemize}
\item Explored the possibility of extending eBPF from the network interfaces
  down to storage mediums.
\item Setup and maintained Ubuntu servers both for the head professor and for
  other researchers.
\end{itemize}

\hfill

\textbf{Wireless Team Lead, \href{https://www.marketsource.com/}{MarketSource,
    Target Mobile}} \textit{Princeton, NJ} \hfill Sep 2015 --- Nov 2016\\
11700 Great Oaks Way, Alpharetta, GA 30022
\begin{itemize}
\item Managed new and existing accounts for Verizon Wireless, AT\&T, Sprint, and
  Comcast XFinity.
\item Maintained relations with Target management to ensure effective sales
  flow, fraud prevention, and organization.
\item Organized and maintained Target Mobile's inventory and assets.
\end{itemize}

\mysection{Projects}
\textbf{Zebra SmartPack}, Senior Design, Stevens Institute of Tech.
\textit{Hoboken, NJ} (C++, Python, Bash) \hfill August 2019 --- May 2020
\begin{itemize}
  \item Worked together with senior design team over the course of 2 semesters.
  \item Designed a machine learning model to identify and categorize types of
    shipping containers.
  \item Used 2D and 3D computer vision technologies to determine position and
    orientation of shipping containers\\ in relation to camera.
  \item Created secure methods of connecting to an insecure system remotely
    through SSH.
\end{itemize}

\hfill

\textbf{Virtual Filesystem}, DexterityDB \textit{Hoboken, NJ} (Rust) \hfill May
2018 --- Aug 2018
\begin{itemize}
\item Designed and implemented a virtual filesystem in Rust.
\item Ensured that it was the minimum needed to work with the database software
  so as to run lean and efficiently.
\end{itemize}

\end{document}
