\documentclass[11pt,letterpaper,roman]{moderncv}
\usepackage[scale=0.8,margin=0.4in]{geometry}

\moderncvstyle{classic}
\moderncvcolor{blue}

\name{Elliot}{Wasem}
\title{Software Engineer}
\address{28 Entwistle Ave}{Nutley, NJ 07110}
\phone[mobile]{1-609-498-2128}
\email{elliotbielwasem@gmail.com}
\homepage{elliot-wasem.github.io/personal-website}
\social[linkedin]{elliot-wasem}
\social[github]{elliot-wasem}

\begin{document}

\makecvtitle

\sethintscolumntowidth{mmm yyyy - mmm yyyy}

\section{Education}
\cventry{2017 -- 2020}{B.S. Computer Science}{Stevens Institute of Technology}{Hoboken, NJ}{}{
    \textit{GPA -- 3.49}
    \begin{itemize}
        \item TA for CS 590 Algorithms, CS 511 Concurrent Programming, CS 442 Database Management Systems, CS 146 Intro to Web Development
        \item Member of Upsilon Pi Epsilon: International Honor Society for the Computing and Information Disciplines
    \end{itemize}
}

\section{Experience}
\cventry{April 2018 -- Current}{Software Engineer}{\href{https://dexteritydb.com}{DexterityDB}}{Hoboken, NJ}{}{
    \begin{itemize}
        \item Developed various parts of database storage engine, with most work done on a virtual filesystem.
        \item Designed and built continuous integration tools such as automated build servers, benchmark servers, and various automation scripts to streamline daily workflow.
        \item Implemented testing scripts to speed up the generation of data as our product was further developed.
        \item Served as the company's Linux expert and server administrator.
    \end{itemize}
}
\cventry{September 2015 -- November 2016}{Wireless Team Lead}{\href{https://www.marketsource.com/}{MarketSource, Target Mobile}}{Princeton, NJ}{}{
    \begin{itemize}
        \item Managed new and existing accounts for Verizon Wireless, AT\&T, Sprint, and Comcast XFinity.
        \item Maintained relations with Target management to ensure effective sales flow, fraud prevention, and organization.
        \item Organized and maintained Target Mobile's inventory and assets.
    \end{itemize}
}

\section{Projects}
\cventry{Personal}{Personal Password Manager}{}{}{}{
  \begin{itemize}
      \item Password manager implemented in Rust.
      \item Uses \href{https://github.com/davatorium/rofi}{Rofi} as a graphical user interface.
      \item Allows locally storing passwords in a secure manner, all locked behind a master password.
      \item The beauty of this password manager is that, even with in-depth knowledge of how it works, it is impossible to read the password file without knowing the master password.
  \end{itemize}
}
\cventry{Personal}{Personal Website}{https://elliot-wasem.github.io/personal-website}{}{}{
    \begin{itemize}
        \item My personal website tries to let the user experience the computer the way I do on a daily basis: through the commandline.
        \item Implemented in ``vanilla'' JavaScript, it provides a handful of custom-implemented commands to let the user browse my credentials in a terminal fashion.
    \end{itemize}
}
\cventry{Academic}{TinyChat, Teaching Assistant, CS511}{}{}{}{
    \begin{itemize}
        \item Designed and setup groundwork for assignment for students in the Fall 2019 semester.
        \item Assignment was to create an IRC chat application, implemented completely in Erlang.
    \end{itemize}
}

\section{Skills}
\cvitem{\textbf{Languages}}{C/C++, Python, Erlang, Java, Rust, Bash, JavaScript}
\cvitem{\textbf{Web \& Cloud}}{HTML5, CSS, MySQL, Kubernetes, GCloud}
\cvitem{\textbf{Misc. Tech}}{Git, Linux, Trello, ZenHub, Emacs, \LaTeX{}}


\end{document}
